Supplementary Information

### 2020-07-03 manuscript/pnas_style/supp.tex

To help reconcile our measure of linked selection, $G(t)$, with familiar
expressions as a reduction in neutral diversity, as parameterized by $N_e$, we
develop some rough approximations here. Note, however, that since linked
selection generates temporal covariance, the overall effect is qualitatively
different than just a simple reduction in $N_e$, as drift alone cannot generate
temporal covariances.  First, we introduce some convenient notation. Let $V_{T}
= \var(p_t - p_0)$ be the total observed \vb{variance} in allele frequency,
$C_{LS} = \sum_{i=0}^{t-1} \sum_{j \ne i}^{t-1} \cov(\Delta p_i, \Delta p_j)$
be the contribution of all pairwise temporal covariances (observable), $V_D$ be
the unobservable drift-only variance in allele frequency, and $V_{LS} =
\sum_{i=0}^{t-1} \var(\Delta_{LS} p_i)$ which is the (unobservable) effect
linked selection has on the variances in allele frequency change. Then,

@@

\vb{Rather than expressing this relationship in terms of variances in allele
frequencies, we can express the same relationship in terms of $N_e$.} In a
neutral Wright--Fisher population, the total variation in allele frequency
change over $t$ generations is

@@

We first investigated the effects of the selected trait's genetic architecture
on temporal covariances and $G(t)$ by neutrally burning in a population for
$10N$ generations, and selecting on the trait with an exponential fitness
function \vb{(where fitness of a trait value $z$ is $w(z) \propto \exp(z)$)}.
The exponential fitness function corresponds to multiplicative selection across
sites and so serves as the simplest directional selection model of a trait to
understand the effects of genetic architecture on the statistics we have used
in the paper.

@@

  \caption{The temporal covariances $\cov(\Delta p_5, \Delta p_t)$ from the
    onset of selection (generation 5) to a later time point $t$, which varies
    along the x-axis, across a variety of different \vb{initial} trait additive
    genetic variances ($V_A$, columns) and number of sites contributing to the
    trait ($L$, rows). Each point is the temporal covariance averaged over 50
    replicate simulations; dark gray points are temporal covariances after the
    onset of selection, and light gray points are before. The red line is a
    loess-smoothed curve through the covariances after the onset of selection.
  Selection on the trait was imposed through an exponential fitness function.}

@@

Overall, we \vb{again see a} finding of \textcite{Buffalo2019-io}: that the
initial expected temporal covariance conditioned on $V_A$, is invariant to the
number of loci determining the trait's value, $L$ (Supplementary Figure
\ref{suppfig:sim-expfit-covs}). We do find some evidence that the decay in
temporal covariance is faster when the trait has a monogenic basis (see the
third column of Supplementary Figure \ref{suppfig:sim-expfit-covs}); this is
expected \vb{since} the selection coefficients are larger for these monogenic
simulations, leading to faster allele frequency changes and a rapid change in
additive genetic variance.

@@

Additionally, we looked at the effect of the \vb{replicate population} size
\vb{drawn from the same} population has on a single population's $G(t)$
trajectories. These simulations had the same $10N$ generation burnin, followed
by a change in population size emulating the bottlenecks associated with
creating selection lines. Overall, we find that smaller population sizes lead
to a reduced $G(t)$ (Supplementary Material Figure
\ref{suppfig:gss-G-sampleN}). This is expected, as the denominator of $G(t)$ is
$\var(p_t - p_0)$, which has an inverse relationship with $N_e$; as replicate
population size is reduced, the proportion of allele frequency change driven by
linked selection is lower, since the rate of drift is increased. To isolate the
effects of varying replicate population size, we also looked at just the
magnitude of temporal covariances (Supplementary Material Figure
\ref{suppfig:gss-covs-sampleN}). We find that smaller replicate population
sizes lead to \emph{larger} temporal covariances. We then looked at the initial
trait variance, which as expected, does not vary with replicate population size
(since all burnin populations had the same size). This implies that the linkage
disequilibria is higher in smaller populations, due to founder effects, which
has the effect inflating the temporal covariance as predicted by our theory
\parencite{Buffalo2019-io}.

@@

Overall, our simulations confirm our hypotheses; see Supplementary Material
Figure \ref{suppfig:convergence-corrs}. We also find that in simulations
\vb{with} a monogenic genetic architecture (i.e. the target number of
trait-affecting loci is $L=1$), the convergence correlations are generally much
weaker than those under a polygenic architecture. However, this effect is
mediated by the line population size; the difference in convergence correlation
between $L = 1$ and $L = 1000$ are more dissimilar when the line population
sizes are larger (compare the first column, last two rows). Like the
convergence correlations calculated on the \textcite{Barghi2019-qy} data, we
find in simulations convergence correlations decay through time. Additionally,
populations selected in opposite directions lead to negative convergence
correlations, as expected. Overall, we find that the convergence correlation is
affected by both genetic architecture and the size of the selected population
lines.

We also wanted to test whether we see similar convergence correlations under
Gaussian stabilizing selection. In these simulations, rather than targeting a
particular $V_A$, we fix the trait mutation rate at $10^{-8}$ (thus region-wide
$\theta = 2000$). Like the exponential directional selection simulations, we
impose directional selection in the same direction across the two populations
(converge), different directions (diverge), and only in one population
(single). We also vary the type (gradual versus sudden) and magnitude of optima
shifts in the two populations. Overall, simulations show convergence
correlations for the sudden optima shifts in Supplementary Figure
\ref{suppfig:convergence-corrs-gss}. Again, optima shifts in the opposite
direction cause negative convergence correlations. We found that for slow
moving optima shifts, the convergence correlations are generally too weak to be
distinguished from zero reliably \vb{(not shown)}.

@@

  \caption{A: The $G(t)$ averaged over 50 replicate simulations with $V_A =
    0.01$ and $L = 1000$. The blue line shows $G(t)$ calculated over ten
    generation blocks, similar to the calculation of temporal covariances of
    the \textcite{Barghi2019-qy} study. The red line shows the average $G(t)$
    estimates when the population is sampled every generation and all
    covariances can contribute to the numerator of $G(t)$. The dashed \vb{dark}
    gray line indicates the $G'(t)$ estimate, which uses the known drift
    effective population size of the simulations. B: The temporal covariances
  calculated each generation (red line) and on ten generation blocks (blue
line) using the same simulation data.}

@@

In our analysis of the \textcite{Barghi2019-qy} data, we describe our statistic
$G(t)$ as a lower bound for two reasons: (1) the population is sequenced every
ten generations, meaning the temporal covariances between adjacent generations
cannot contribute to the numerator of $G(t)$ but contributes to the
denominator, and (2) the estimate of $G(t)$ ignores linked selection's
contribution to the per-generation variance in allele frequency change. \vb{ In
\textcite{Buffalo2019-io}, we define an alternative estimator
that includes selection's effects on these variance terms,

\begin{equation}
  G'(t) = 1 - \frac{t\E(p_0(1-p_0))}{2 {N_e}\var(p_t - p_0)},
\end{equation}
%
which can be calculated when the drift-effective population size $N_e$ can
be estimated (see equation 26 in \cite{Buffalo2019-io} for details).}

To verify that $G(t)$ estimated every ten generations is indeed a lower bound,
we used a simulation procedure similar to the exponential fitness function
simulations (described in Supplementary Material Section
\ref{supp:genetic-arch}), and calculated the temporal covariances and $G(t)$
both each generation, and every ten generations. Unlike the simulations
described in \ref{supp:genetic-arch} \vb{where selection began at $10N+5$
generations}, selection \vb{starts at generation $10N$ here}, and used trait
$V_A = 0.01$ and targeted $L = 1000$ sites affecting the trait.

First, comparing $G(t)$ when sampling population frequencies every generation
versus every ten generations, we confirm that the ten-generation block $G(t)$
is a lower bound of the $G(t)$ trajectory when sampling is every generation
(red and blue lines in Supplementary Figure \ref{suppfig:supp-blocks}A).
Furthermore, since we control the population size \vb{and reproductive sampling
scheme} in our simulations at $N = 1000$ diploids, we know the drift-effective
population size in the absence of selection, \vb{which allows us to estimate
$G'(t)$}. Plugging in the drift-effective population size $N_e = 1000$ into
the expression for $G'(t)$ and using the $\var(p_t - p_0)$ calculated for
different $t$'s, we see that $G(t)$ calculated every generation does not
account for linked selection's inflation of $\var(\Delta p_t)$ and
underestimates the true impact of linked selection as expected (dashed gray
line in Supplementary Figure \ref{suppfig:supp-blocks}A).

@@

We simulated background selection in a 50 megabase region, where deleterious
alleles are randomly introduced by mutation. Following background selection
literature
\parencite{Charlesworth1993-gb,Nordborg1996-nq,Hudson1994-oh,Hudson1995-xc}, we
parameterize the mutation rate as the total number of deleterious mutations
introduced per diploid genome, per generation, and simulate values $U = \{0.5,
1.0, 1.5\}$. Note that for our 50Mb region, our choice of BGS $U$ parameters
are on the higher end of the spectrum expected for \emph{Drosophila}, but we
wanted to ensure the strength was sufficient to see a signal. Note that if $U
\approx 1.6$ \parencite{Elyashiv2016-vt}, and the \emph{Drosophila} genome is
$\approx 140$Mb, our region is $\approx 36\%$ of the genome; this implies a
reasonable $U$ for our region is $U \approx 0.57$, which is close to the bottom
end of our parameter range. We also vary the strength of selection against the
deleterious mutations, $s = \{0.01, 0.05, 0.1\}$, as well as different
recombination rates ($r_{bp} = \{10^{-7}, 10^{-8}\}$).  Like other simulations,
we burnin the population for $10N$ generations under backgrounds selection.
Overall, we find background selection does create temporal covariance
(Supplementary Material Figure \ref{suppfig:supp-bgs-covs}), which are stronger
under (1) higher deleterious mutation rates and (2) larger selection
coefficients. This latter point initially seems at odds with background
selection theory, as the level of pairwise diversity in a region under strong
background selection is invariant with respect to the selection coefficient.
However, looking at the background selection $G(t)$ trajectories, we find that
over time, background selection appears to trend towards an \vb{asymptote} in
the $r_{BP} = 10^{-7}$ subfigure, and reaches an equilibrium in the $r_{BP} =
10^{-8}$ subfigure that seems reasonably invariant to the choice of $s$
(Supplementary Material Figure \ref{suppfig:supp-bgs-g-fix}). We believe that
these observations can be reconciled by $Cov(\Delta p_t,~ \Delta
p_{t^{\prime}})$ being larger for larger $s$ when $|t^{\prime}-t|$ is small,
but also decaying more rapidly with $|t^{\prime}-t|$, such that the overall
contribution of selection to allele frequency variance is invariant to $s$ (for
strong background selection).  However, further work is needed to fully explore
and understand the temporal covariance dynamics of background selection.

@@

  \caption{The trajectories of $G(t)$ through time under background selection,
    under different recombination rates ($r_{BP}$, rows), selection
    coefficients ($s$), and deleterious mutation rates ($U$). The first column
    \vb{fixes} $U = 1.0$, and $s$ varies, while in the second column $s=0.05$
    is held constant, and $U$ varies. \vb{$G(t)$ is} calculated using both
  including fixed sites (solid lines) and not including fixed sites (dashed
lines).}

@@

Finally, we found in \vb{processing these background selection simulation
results} that including or excluding sites fixed or lost through time can lead
to differences in the estimated $G(t)$ trajectories and temporal covariance. We
discuss this extensively in a subsequent section, Supplementary Materials
Section \ref{supp:fixation}.

@@

We also explored how directional truncation selection generates temporal
covariances. In these simulations we select the top 10\%, 25\%, or 50\% of the
phenotypic distribution of individuals to form the next generation. We burnin
these simulations using a neutral burnin routine, where trait alleles are
selectively neutral until directional selection is imposed. More extreme
directional truncation selection generated larger initial covariances
(Supplementary Material Figure \ref{suppfig:supp-trunc}B).  However, weaker
truncation selection generated more sustained positive covariances and so
\vb{have} a larger long-term impact on the variance in allele frequency change.
We again noticed fixation or loss of sites has a strong effect on temporal
covariance and $G(t)$ under truncation selection.  Here, since only a
(potentially small) fraction of individuals contribute to the next generation,
sites can fix over very short timescales.  Furthermore, the small number of
effective breeders contributing to the next generation shrinks $N_e$
considerably, which increases $\var(p_t - p_0)$, the denominator of $G(t)$. We
see both the effect of handling fixed/lost sites differently and the faster
rate of drift in Supplementary Materials Figure \ref{suppfig:supp-trunc}A,
where weaker truncation selection actually has higher levels of $G(t)$. Looking
just at temporal covariances, we find that stronger truncation selection (e.g.
a smaller tail of individuals selected) does lead to greater temporal
covariances. Overall, these truncation selection simulations demonstrate the
value of considering both absolute measures of selection's effect on allele
frequency changes, i.e. temporal covariance, as well as measures relative to
drift, i.e. the $G(t)$ trajectories. While selecting a smaller tail of
individuals is associated with \emph{stronger} selection, it also is leading to
a faster rate of drift, which can distort conclusions inferred from considering
the $G(t)$ trajectories alone.

>>>>

To help reconcile our measure of linked selection, $G(t)$, with familiar
expressions as a reduction in neutral diversity, as parameterized by $N_e$, we
develop some rough approximations here. Note, however, that since linked
selection generates temporal covariance, the overall effect is qualitatively
different than just a simple reduction in $N_e$, as drift alone cannot generate
temporal covariances.  First, we introduce some convenient notation. Let $V_{T}
= \var(p_t - p_0)$ be the total observed variance in allele frequency,
$C_{LS} = \sum_{i=0}^{t-1} \sum_{j \ne i}^{t-1} \cov(\Delta p_i, \Delta p_j)$
be the contribution of all pairwise temporal covariances (observable), $V_D$ be
the unobservable drift-only variance in allele frequency, and $V_{LS} =
\sum_{i=0}^{t-1} \var(\Delta_{LS} p_i)$ which is the (unobservable) effect
linked selection has on the variances in allele frequency change. Then,

@@

Rather than expressing this relationship in terms of variances in allele
frequencies, we can express the same relationship in terms of $N_e$. In a
neutral Wright--Fisher population, the total variation in allele frequency
change over $t$ generations is

@@

We first investigated the effects of the selected trait's genetic architecture
on temporal covariances and $G(t)$ by neutrally burning in a population for
$10N$ generations, and selecting on the trait with an exponential fitness
function (where fitness of a trait value $z$ is $w(z) \propto \exp(z)$).
The exponential fitness function corresponds to multiplicative selection across
sites and so serves as the simplest directional selection model of a trait to
understand the effects of genetic architecture on the statistics we have used
in the paper.

@@

  \caption{The temporal covariances $\cov(\Delta p_5, \Delta p_t)$ from the
    onset of selection (generation 5) to a later time point $t$, which varies
    along the x-axis, across a variety of different initial trait additive
    genetic variances ($V_A$, columns) and number of sites contributing to the
    trait ($L$, rows). Each point is the temporal covariance averaged over 50
    replicate simulations; dark gray points are temporal covariances after the
    onset of selection, and light gray points are before. The red line is a
    loess-smoothed curve through the covariances after the onset of selection.
  Selection on the trait was imposed through an exponential fitness function.}

@@

Overall, we again see a finding of \textcite{Buffalo2019-io}: that the
initial expected temporal covariance conditioned on $V_A$, is invariant to the
number of loci determining the trait's value, $L$ (Supplementary Figure
\ref{suppfig:sim-expfit-covs}). We do find some evidence that the decay in
temporal covariance is faster when the trait has a monogenic basis (see the
third column of Supplementary Figure \ref{suppfig:sim-expfit-covs}); this is
expected since the selection coefficients are larger for these monogenic
simulations, leading to faster allele frequency changes and a rapid change in
additive genetic variance.

@@

Additionally, we looked at the effect of the replicate population size
drawn from the same population has on a single population's $G(t)$
trajectories. These simulations had the same $10N$ generation burnin, followed
by a change in population size emulating the bottlenecks associated with
creating selection lines. Overall, we find that smaller population sizes lead
to a reduced $G(t)$ (Supplementary Material Figure
\ref{suppfig:gss-G-sampleN}). This is expected, as the denominator of $G(t)$ is
$\var(p_t - p_0)$, which has an inverse relationship with $N_e$; as replicate
population size is reduced, the proportion of allele frequency change driven by
linked selection is lower, since the rate of drift is increased. To isolate the
effects of varying replicate population size, we also looked at just the
magnitude of temporal covariances (Supplementary Material Figure
\ref{suppfig:gss-covs-sampleN}). We find that smaller replicate population
sizes lead to \emph{larger} temporal covariances. We then looked at the initial
trait variance, which as expected, does not vary with replicate population size
(since all burnin populations had the same size). This implies that the linkage
disequilibria is higher in smaller populations, due to founder effects, which
has the effect inflating the temporal covariance as predicted by our theory
\parencite{Buffalo2019-io}.

@@

Overall, our simulations confirm our hypotheses; see Supplementary Material
Figure \ref{suppfig:convergence-corrs}. We also find that in simulations
with a monogenic genetic architecture (i.e. the target number of
trait-affecting loci is $L=1$), the convergence correlations are generally much
weaker than those under a polygenic architecture. However, this effect is
mediated by the line population size; the difference in convergence correlation
between $L = 1$ and $L = 1000$ are more dissimilar when the line population
sizes are larger (compare the first column, last two rows). Like the
convergence correlations calculated on the \textcite{Barghi2019-qy} data, we
find in simulations convergence correlations decay through time. Additionally,
populations selected in opposite directions lead to negative convergence
correlations, as expected. Overall, we find that the convergence correlation is
affected by both genetic architecture and the size of the selected population
lines.

We also wanted to test whether we see similar convergence correlations under
Gaussian stabilizing selection. In these simulations, rather than targeting a
particular $V_A$, we fix the trait mutation rate at $10^{-8}$ (thus region-wide
$\theta = 2000$). Like the exponential directional selection simulations, we
impose directional selection in the same direction across the two populations
(converge), different directions (diverge), and only in one population
(single). We also vary the type (gradual versus sudden) and magnitude of optima
shifts in the two populations. Overall, simulations show convergence
correlations for the sudden optima shifts in Supplementary Figure
\ref{suppfig:convergence-corrs-gss}. Again, optima shifts in the opposite
direction cause negative convergence correlations. We found that for slow
moving optima shifts, the convergence correlations are generally too weak to be
distinguished from zero reliably (not shown).

@@

  \caption{A: The $G(t)$ averaged over 50 replicate simulations with $V_A =
    0.01$ and $L = 1000$. The blue line shows $G(t)$ calculated over ten
    generation blocks, similar to the calculation of temporal covariances of
    the \textcite{Barghi2019-qy} study. The red line shows the average $G(t)$
    estimates when the population is sampled every generation and all
    covariances can contribute to the numerator of $G(t)$. The dashed dark
    gray line indicates the $G'(t)$ estimate, which uses the known drift
    effective population size of the simulations. B: The temporal covariances
  calculated each generation (red line) and on ten generation blocks (blue
line) using the same simulation data.}

@@

In our analysis of the \textcite{Barghi2019-qy} data, we describe our statistic
$G(t)$ as a lower bound for two reasons: (1) the population is sequenced every
ten generations, meaning the temporal covariances between adjacent generations
cannot contribute to the numerator of $G(t)$ but contributes to the
denominator, and (2) the estimate of $G(t)$ ignores linked selection's
contribution to the per-generation variance in allele frequency change. In
\textcite{Buffalo2019-io}, we define an alternative estimator
that includes selection's effects on these variance terms,

\begin{equation}
  G'(t) = 1 - \frac{t\E(p_0(1-p_0))}{2 {N_e}\var(p_t - p_0)},
\end{equation}
%
which can be calculated when the drift-effective population size $N_e$ can
be estimated (see equation 26 in \cite{Buffalo2019-io} for details).

To verify that $G(t)$ estimated every ten generations is indeed a lower bound,
we used a simulation procedure similar to the exponential fitness function
simulations (described in Supplementary Material Section
\ref{supp:genetic-arch}), and calculated the temporal covariances and $G(t)$
both each generation, and every ten generations. Unlike the simulations
described in \ref{supp:genetic-arch} where selection began at $10N+5$
generations, selection starts at generation $10N$ here, and used trait
$V_A = 0.01$ and targeted $L = 1000$ sites affecting the trait.

First, comparing $G(t)$ when sampling population frequencies every generation
versus every ten generations, we confirm that the ten-generation block $G(t)$
is a lower bound of the $G(t)$ trajectory when sampling is every generation
(red and blue lines in Supplementary Figure \ref{suppfig:supp-blocks}A).
Furthermore, since we control the population size and reproductive sampling
scheme in our simulations at $N = 1000$ diploids, we know the drift-effective
population size in the absence of selection, which allows us to estimate
$G'(t)$. Plugging in the drift-effective population size $N_e = 1000$ into
the expression for $G'(t)$ and using the $\var(p_t - p_0)$ calculated for
different $t$'s, we see that $G(t)$ calculated every generation does not
account for linked selection's inflation of $\var(\Delta p_t)$ and
underestimates the true impact of linked selection as expected (dashed gray
line in Supplementary Figure \ref{suppfig:supp-blocks}A).

@@

We simulated background selection in a 50 megabase region, where deleterious
alleles are randomly introduced by mutation. Following background selection
literature
\parencite{Charlesworth1993-gb,Nordborg1996-nq,Hudson1994-oh,Hudson1995-xc}, we
parameterize the mutation rate as the total number of deleterious mutations
introduced per diploid genome, per generation, and simulate values $U = \{0.5,
1.0, 1.5\}$. Note that for our 50Mb region, our choice of BGS $U$ parameters
are on the higher end of the spectrum expected for \emph{Drosophila}, but we
wanted to ensure the strength was sufficient to see a signal. Note that if $U
\approx 1.6$ \parencite{Elyashiv2016-vt}, and the \emph{Drosophila} genome is
$\approx 140$Mb, our region is $\approx 36\%$ of the genome; this implies a
reasonable $U$ for our region is $U \approx 0.57$, which is close to the bottom
end of our parameter range. We also vary the strength of selection against the
deleterious mutations, $s = \{0.01, 0.05, 0.1\}$, as well as different
recombination rates ($r_{bp} = \{10^{-7}, 10^{-8}\}$).  Like other simulations,
we burnin the population for $10N$ generations under backgrounds selection.
Overall, we find background selection does create temporal covariance
(Supplementary Material Figure \ref{suppfig:supp-bgs-covs}), which are stronger
under (1) higher deleterious mutation rates and (2) larger selection
coefficients. This latter point initially seems at odds with background
selection theory, as the level of pairwise diversity in a region under strong
background selection is invariant with respect to the selection coefficient.
However, looking at the background selection $G(t)$ trajectories, we find that
over time, background selection appears to trend towards an asymptote in
the $r_{BP} = 10^{-7}$ subfigure, and reaches an equilibrium in the $r_{BP} =
10^{-8}$ subfigure that seems reasonably invariant to the choice of $s$
(Supplementary Material Figure \ref{suppfig:supp-bgs-g-fix}). We believe that
these observations can be reconciled by $Cov(\Delta p_t,~ \Delta
p_{t^{\prime}})$ being larger for larger $s$ when $|t^{\prime}-t|$ is small,
but also decaying more rapidly with $|t^{\prime}-t|$, such that the overall
contribution of selection to allele frequency variance is invariant to $s$ (for
strong background selection).  However, further work is needed to fully explore
and understand the temporal covariance dynamics of background selection.

@@

  \caption{The trajectories of $G(t)$ through time under background selection,
    under different recombination rates ($r_{BP}$, rows), selection
    coefficients ($s$), and deleterious mutation rates ($U$). The first column
    fixes $U = 1.0$, and $s$ varies, while in the second column $s=0.05$
    is held constant, and $U$ varies. $G(t)$ is calculated using both
  including fixed sites (solid lines) and not including fixed sites (dashed
lines).}

@@

Finally, we found in processing these background selection simulation
results that including or excluding sites fixed or lost through time can lead
to differences in the estimated $G(t)$ trajectories and temporal covariance. We
discuss this extensively in a subsequent section, Supplementary Materials
Section \ref{supp:fixation}.

@@

We also explored how directional truncation selection generates temporal
covariances. In these simulations we select the top 10\%, 25\%, or 50\% of the
phenotypic distribution of individuals to form the next generation. We burnin
these simulations using a neutral burnin routine, where trait alleles are
selectively neutral until directional selection is imposed. More extreme
directional truncation selection generated larger initial covariances
(Supplementary Material Figure \ref{suppfig:supp-trunc}B).  However, weaker
truncation selection generated more sustained positive covariances and so
have a larger long-term impact on the variance in allele frequency change.
We again noticed fixation or loss of sites has a strong effect on temporal
covariance and $G(t)$ under truncation selection.  Here, since only a
(potentially small) fraction of individuals contribute to the next generation,
sites can fix over very short timescales.  Furthermore, the small number of
effective breeders contributing to the next generation shrinks $N_e$
considerably, which increases $\var(p_t - p_0)$, the denominator of $G(t)$. We
see both the effect of handling fixed/lost sites differently and the faster
rate of drift in Supplementary Materials Figure \ref{suppfig:supp-trunc}A,
where weaker truncation selection actually has higher levels of $G(t)$. Looking
just at temporal covariances, we find that stronger truncation selection (e.g.
a smaller tail of individuals selected) does lead to greater temporal
covariances. Overall, these truncation selection simulations demonstrate the
value of considering both absolute measures of selection's effect on allele
frequency changes, i.e. temporal covariance, as well as measures relative to
drift, i.e. the $G(t)$ trajectories. While selecting a smaller tail of
individuals is associated with \emph{stronger} selection, it also is leading to
a faster rate of drift, which can distort conclusions inferred from considering
the $G(t)$ trajectories alone.
